Early Observations of \abc:\\ \textbf{a Type Ia Supernova Featuring Either} Strong Ejecta Mixing and/or Interaction with Diffuse Material

### 2017-10-26 doc/ms.tex
Remove a few sentences following (reasonable) objections from the referee

To determine the best fit parameters, we search a large grid over $t_0$,
$\alpha$, and the proportionality constant, and minimize $\chi^2$. The
modeling results show that the SN flux rises approximately linearly between
$t=-18\,\textrm{d}$ and $t=-15\,\textrm{d}$. Figure \ref{fig:early_lc_fit}
shows the best-fit result and the joint marginal distribution of $t_0$ and
$\alpha$. From the best-fit model we obtain $\alpha=0.98 \pm ^{0.16}_{0.14}$
and $t_0=-17.91 \pm ^{0.07}_{0.15}$ d, where the uncertainties represent the
marginalized 95\% confidence intervals. Our first detection of \abc\ occurred
$\sim$${0.15}\,\textrm{d}$ after the SN first light. In the analysis that
follows, the precise values of the best-fit parameters are not important. The
critical finding here is that $\alpha \approx 1$ and $t_0 \approx -18 \,
\mathrm{d}$.

@@

Relative to the nearby, normal SN\,2011fe, we have identified several distinct characteristics of the early evolution of \abc, including: (i) a near-linear photometric rise, (ii) a qualitatively short, or possibly absent, dark phase, assuming $v_\mathrm{ph} \propto t^{-0.22}$, (iii) the presence of strong \ion{C}{2} absorption, and (iv) blue and non-evolving $(B - V)_0$ color in the week after explosion. While most SNe Ia are powered purely by radioactive decay, the observed radiation shortly after explosion can also include contributions 
from SN shock cooling or the collision of the SN ejecta with a non-degenerate companion or diffuse material. Here we consider those scenarios as a possible explanation for the early behavior of \abc.

@@

\subsection{Interaction with Diffuse Material}

@@

Having examined other possibilities we now consider whether the unusual properties of \abc\ can be explained simply by invoking strong mixing in the SN ejecta. Strong mixing leads to a shorter dark phase than would otherwise be observed. Here we additionally examine whether strong mixing can explain the rapid, near-linear rise in the light curve.

@@

While the models from \citet{2016ApJ...826...96P} provide a good match to the optical photometric evolution of \abc, they consistently overpredict the flux in the UV. The models shown in Figure~\ref{fig:Ni56LC} also overpredict the photospheric velocity of \abc\ by $\sim$2--3,000$\; \mathrm{km \; s}^{-1}$. These discrepancies may be accounted for following an improved treatment of line-blanketing and a reduction in the model explosion energy, respectively. Future modeling efforts may improve the match between the simulations and observations for \abc.

>>>>

To determine the best fit parameters, we search a large grid over $t_0$,
$\alpha$, and the proportionality constant, and minimize $\chi^2$. The
modeling results show that the SN flux rises approximately linearly between
$t=-18\,\textrm{d}$ and $t=-15\,\textrm{d}$. Figure \ref{fig:early_lc_fit}
shows the best-fit result and the joint marginal distribution of $t_0$ and
$\alpha$. From the best-fit model we obtain $\alpha=0.98 \pm ^{0.16}_{0.14}$
and $t_0=-17.91 \pm ^{0.07}_{0.15}$ d, where the uncertainties represent the
marginalized 95\% confidence intervals \textit{THIS IS NOT THE CORRECT MARGINALIZED UNCERTAINTY}. Our first detection of \abc\ occurred
$\sim$${0.15}\,\textrm{d}$ after the SN first light. In the analysis that
follows, the precise values of the best-fit parameters are not important. The
critical finding here is that $\alpha \approx 1$ and $t_0 \approx -18 \,
\mathrm{d}$.

@@

Relative to the nearby, normal SN\,2011fe, we have identified several distinct characteristics of the early evolution of \abc, including: (i) a near-linear photometric rise, (ii) a qualitatively short, or possibly absent, dark phase, assuming $v_\mathrm{ph} \propto t^{-0.22}$, (iii) the presence of strong \ion{C}{2} absorption, and (iv) blue and non-evolving $(B - V)_0$ color in the week after explosion. While most SNe Ia are powered purely by radioactive decay, the observed radiation shortly after explosion can also include contributions 
from SN shock cooling or the collision of the SN ejecta with a non-degenerate companion or \textbf{nearby, unbound} material. Here we consider those scenarios as a possible explanation for the early behavior of \abc.

@@

\subsection{Interaction with \textbf{Nearby, Unbound} Material}

@@

Having examined other possibilities we now consider whether the unusual
properties of \abc\ can be explained simply by invoking strong mixing in the
SN ejecta. Strong mixing leads to a shorter dark phase than would otherwise
be observed. \textbf{We also consider} whether strong mixing can explain the
rapid, near-linear rise in the light curve.

@@

While the models from \citet{2016ApJ...826...96P} provide a good match to the
optical photometric evolution of \abc, they consistently overpredict the flux
in the UV. The models shown in Figure~\ref{fig:Ni56LC} also overpredict the
photospheric velocity of \abc\ by $\sim$2--3,000$\; \mathrm{km \; s}^{-1}$.
Future modeling efforts may improve the match between the simulations and
observations for \abc.
